Hypothesis tests for multiple responses regression: effect of probiotics on addiction and binge eating disorder.

### 2022-07-27 5_artigos/statistic-in-medicine/draft/ARXIV/draft-sm-lineu.tex
organiza drafts

\jnlcitation{\cname{%
\author{Freitas LAC}, 
\author{Carlos LO},
\author{Campos ACL} and 
\author{Bonat WH}} (\cyear{2022}), 
\ctitle{Wald test to evaluate regression and dispersion parameters in multivariate covariance generalized linear models}, \cjournal{Statistics in Medicine}}

@@

We present the dataset in \autoref{sec2}. In \autoref{sec3} we present the review of the general structure and estimation of the parameters of a McGLM, based on the ideas of Bonat and Jørgensen \cite{Bonat16}. In \autoref{sec4} our proposal is presented with the details of the Wald test to evaluate assumptions about parameters of a McGLM. In \autoref{sec5} we present the results of the performance evaluation of the proposed test based on a simulation study. In the \autoref{sec6} we apply the model and present the main results of the analysis of the data from the clinical study that aims to evaluate the use of probiotics in the control of addiction and binge eating disorder in patients undergoing bariatric surgery. Finally, the main results are discussed in \autoref{sec7}, including some directions for future investigations.

@@

\begin{figure}[h]
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{Exploratory graphic analysis: (a) YFAS histogram, (b) YFAS boxplots as a function of group, (c) YFAS boxplots as a function of moment, (d) BES histogram, (b) BES boxplots as a function of group, (c) BES boxplots as a function of moment. The asterisk in the boxplots indicates the mean.\label{fig1}}
\end{figure}

@@

@@

@@

\begin{figure}[h]
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{Simulation study results for the regression parameters.\label{fig2}}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{Simulation study results for the dispersion parameters.\label{fig3}}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{Histogram of Pearson residuals by response.\label{fig4}}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{Pearson residuals versus predicted plot with smooth trend line for each response.\label{fig5}}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{Graph of model predicted for each time and group combination.\label{fig6}}
\end{figure}

@@

@@

@@

@@

@@

% TEXT TABLES ----------------------------------------------------------

% ----------------------------------------------------------------------
% table 1

\begin{table}[H]
\centering
\begin{tabular}{ccccc}
\hline
\multirow{2}{*}{Group} & \multirow{2}{*}{Moment}  & \multirow{2}{*}{n} & YFAS                  & BES                   \\ \cline{4-5} 
                       &                          &                    & Mean (standard deviation) & Mean (standard deviation) \\ \hline
Placebo                & T0                       & 33                 & 0.37 (0.26)           & 0.24 (0.20)           \\
Placebo                & T1                       & 32                 & 0.11 (0.15)           & 0.09 (0.10)           \\
Placebo                & T2                       & 22                 & 0.16 (0.15)           & 0.10 (0.12)           \\
Probiotic              & T0                       & 38                 & 0.49 (0.24)           & 0.32 (0.18)           \\
Probiotic              & T1                       & 37                 & 0.09 (0.12)           & 0.10 (0.08)           \\
Probiotic              & T2                       & 22                 & 0.10 (0.14)           & 0.07 (0.09)           \\ \hline
\end{tabular}
\caption{Number of individuals, mean and standard deviation for YFAS and BES for each combination of group and time point.}
\label{tab:tab1}
\end{table}

% ----------------------------------------------------------------------
% table 2

\begin{table}[H]
\centering
\begin{tabular}{ccc}
\hline
Distribution & Link function     & Variance function \\ \hline
Normal       & Identity          & Constant           \\
Poisson      & Logarithmic       & Tweedie             \\
Bernoulli    & Logit             & Binomial            \\ \hline
\end{tabular}
\caption{Link and variance functions used in the models for each simulated distribution.}
\label{tab2}
\end{table}

% ----------------------------------------------------------------------
% table 3

\begin{table}[H]
\centering
\begin{tabular}{c|cccccc}
\hline
\multirow{2}{*}{Parameter} & \multicolumn{3}{c}{YFAS}                                                                                             & \multicolumn{3}{c}{BES}                                                                         \\ \cline{2-7} 
                           & Estimate & \begin{tabular}[c]{@{}c@{}}Confidence \\ interval\end{tabular} & \multicolumn{1}{c|}{p-value}        & Estimate & \begin{tabular}[c]{@{}c@{}}Confidence \\ interval\end{tabular} & p-value        \\ \hline
$\beta_0$                  & -0.54      & (-0.87;-0.22)                                                     & \multicolumn{1}{c|}{\textless 0.01} & -1.13      & (-1.44;-0.83)                                                     & \textless 0.01 \\
$\beta_1$                  & -1.55      & (-2.17;-0.94)                                                     & \multicolumn{1}{c|}{\textless 0.01} & -1.16      & (-1.62;-0.69)                                                     & \textless 0.01 \\
$\beta_2$                  & -1.13      & (-1.75;-0.51)                                                     & \multicolumn{1}{c|}{\textless 0.01} & -1.05      & (-1.58;-0.52)                                                     & \textless 0.01 \\
$\beta_3$                  & 0.49       & (0.05;0.93)                                                       & \multicolumn{1}{c|}{0.0284} & 0.37       & (-0.03;0.77)                                                      & 0.0733           \\
$\beta_4$                  & -0.73      & (-1.60;0.14)                                                      & \multicolumn{1}{c|}{0.0}            & -0.33      & (-0.96;0.30)                                                      & 0.3081           \\
$\beta_5$                  & -0.98      & (-1.93;-0.03)                                                     & \multicolumn{1}{c|}{0.0429} & -0.80      & (-1.58;-0.02)                                                     & 0.0449 \\
$\tau_0$                   & 0.18       & (0.01;0.35)                                                       & \multicolumn{1}{c|}{0.0411} & 0.17       & (0.00;0.34)                                                       & 0.0458           \\
$\tau1$                    & 0.01       & (-0.02;0.04)                                                      & \multicolumn{1}{c|}{0.5718}           & 0.04       & (-0.01;0.10)                                                      & 0.1357           \\
$p$                        & 0.91       & (0.47;1.34)                                                       & \multicolumn{1}{c|}{\textless 0.05} & 1.23       & (0.77;1.68)                                                       & \textless 0.05 \\ \hline
\end{tabular}
\caption{Parameter estimates, 95\% confidence intervals and p-values of the model.}
\label{tab3}
\end{table}

% ----------------------------------------------------------------------
% table 4

\begin{table}[H]
\centering
\begin{tabular}{cccc}
\hline
Variable      & Degrees of freedom & Chi-square   & p-value        \\ \hline
Intercept     & 2                  & 53.1581      & \textless 0.01 \\
Moment        & 8                  & 139.0161     & \textless 0.01 \\
Group         & 6                  & 8.4928       & 0.2042         \\
Moment*Group  & 4                  & 6.9923       & 0.1363         \\ \hline
\end{tabular}
\caption{Type II multivariate analysis of variance.}
\label{tab4}
\end{table}

% ----------------------------------------------------------------------
% table 5

\begin{table}[H]
\centering
\begin{tabular}{c|c|cc|cc}
\hline
              &                    & \multicolumn{2}{c|}{YFAS}     & \multicolumn{2}{c}{BES}       \\ \hline
Variable      & Degrees of freedom & Chi-square   & p-value        & Chi-square   & p-value        \\ \hline
Intercept     & 1                  & 10.6128      & \textless 0.01 & 53.1473      & \textless 0.01 \\
Moment        & 4                  & 102.9875     & \textless 0.01 & 99.5681      & \textless 0.01 \\
Group         & 3                  & 6.6837       & 0.0827         & 5.3083       & 0.1506         \\
Moment*Group  & 2                  & 5.5984       & 0.0609         & 4.2477       & 0.1196         \\ \hline
\end{tabular}
\caption{Type II univariate analysis of variance.}
\label{tab5}
\end{table}

% ----------------------------------------------------------------------
% table 6

\begin{table}[H]
\centering
\begin{tabular}{cccc}
\hline
Contrast  & Degrees of freedom & Chi-square   & p-value        \\ \hline
T0-T1     & 2                  & 97.9874      & \textless 0.01 \\
T0-T2     & 2                  & 67.2462      & \textless 0.01 \\
T1-T2     & 2                  & 2.4730       & 0.8712         \\ \hline
\end{tabular}
\caption{Two-by-two comparisons between moments for both responses.}
\label{tab6}
\end{table}

% ----------------------------------------------------------------------
% table 7

\begin{table}[H]
\centering
\begin{tabular}{cccc}
\hline
Contrast                 & Degrees of freedom & Chi-square   & p-value \\ \hline
T0:Placebo-T0:Probiotic  & 2                  & 5.5819       & 0.9204  \\
T1:Placebo-T1:Probiotic  & 2                  & 0.6096       & 1       \\
T2:Placebo-T2:Probiotic  & 2                  & 1.7645       & 1       \\ \hline
\end{tabular}
\caption{Two-by-two comparisons between groups for each time point for both responses.}
\label{tab7}
\end{table}

% ----------------------------------------------------------------------
% table 8

\begin{table}[H]
\centering
\begin{tabular}{cccc}
\hline
Variable               & Degrees of freedom & Chi-square & p-value        \\ \hline
$\tau_0$ & 2                  & 7.1936       & 0.0274  \\
$\tau_1$ & 2                  & 2.3201       & 0.3135         \\ \hline
\end{tabular}
\caption{Type III multivariate analysis of variance for dispersion parameters.}
\label{tab8}
\end{table}

% ----------------------------------------------------------------------

@@

\begin{table}[H]
\centering
\begin{tabular}{c|cccc}
\hline
Null hypothesis & $\beta_0$ & $\beta_1$ & $\beta_2$ & $\beta_3$ \\ \hline
$H_{01}$      & 5         & 0         & 0         & 0         \\
$H_{02}$      & 4.85      & 0.05      & 0.05      & 0.05      \\
$H_{03}$      & 4.7       & 0.1       & 0.1       & 0.1       \\
$H_{04}$      & 4.55      & 0.15      & 0.15      & 0.15      \\
$H_{05}$      & 4.4       & 0.2       & 0.2       & 0.2       \\
$H_{06}$      & 4.25      & 0.25      & 0.25      & 0.25      \\
$H_{07}$      & 4.1       & 0.3       & 0.3       & 0.3       \\
$H_{08}$      & 3.95      & 0.35      & 0.35      & 0.35      \\
$H_{09}$      & 3.8       & 0.4       & 0.4       & 0.4       \\
$H_{10}$      & 3.65      & 0.45      & 0.45      & 0.45      \\
$H_{11}$      & 3.5       & 0.5       & 0.5       & 0.5       \\
$H_{12}$      & 3.35      & 0.55      & 0.55      & 0.55      \\
$H_{13}$      & 3.2       & 0.6       & 0.6       & 0.6       \\
$H_{14}$      & 3.05      & 0.65      & 0.65      & 0.65      \\
$H_{15}$      & 2.9       & 0.7       & 0.7       & 0.7       \\
$H_{16}$      & 2.75      & 0.75      & 0.75      & 0.75      \\
$H_{17}$      & 2.6       & 0.8       & 0.8       & 0.8       \\
$H_{18}$      & 2.45      & 0.85      & 0.85      & 0.85      \\
$H_{19}$      & 2.3       & 0.9       & 0.9       & 0.9       \\
$H_{20}$      & 2.15      & 0.95      & 0.95      & 0.95      \\ \hline
\end{tabular}
\caption{Tested hypotheses for regression parameters in models with response following Normal distribution.}
\label{tab:hipoteses_beta_normal}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{c|cccc}
\hline
Null hypothesis & $\beta_0$ & $\beta_1$ & $\beta_2$ & $\beta_3$ \\ \hline
$H_{01}$      & 2.3       & 0         & 0         & 0         \\
$H_{02}$      & 2.25      & 0.017     & 0.017     & 0.017     \\
$H_{03}$      & 2.2       & 0.033     & 0.033     & 0.033     \\
$H_{04}$      & 2.15      & 0.05      & 0.05      & 0.05      \\
$H_{05}$      & 2.10      & 0.067     & 0.067     & 0.067     \\
$H_{06}$      & 2.05      & 0.083     & 0.083     & 0.083     \\
$H_{07}$      & 2         & 0.1       & 0.1       & 0.1       \\
$H_{08}$      & 1.95      & 0.117     & 0.117     & 0.117     \\
$H_{09}$      & 1.9       & 0.133     & 0.133     & 0.133     \\
$H_{10}$      & 1.85      & 0.15      & 0.15      & 0.15      \\
$H_{11}$      & 1.8       & 0.167     & 0.167     & 0.167     \\
$H_{12}$      & 1.75      & 0.167     & 0.167     & 0.167     \\
$H_{13}$      & 1.7       & 0.2       & 0.2       & 0.2       \\
$H_{14}$      & 1.65      & 0.217     & 0.217     & 0.217     \\
$H_{15}$      & 1.6       & 0.233     & 0.233     & 0.233     \\
$H_{16}$      & 1.55      & 0.25      & 0.25      & 0.25      \\
$H_{17}$      & 1.5       & 0.267     & 0.267     & 0.267     \\
$H_{18}$      & 1.45      & 0.283     & 0.283     & 0.283     \\
$H_{19}$      & 1.4       & 0.3       & 0.3       & 0.3       \\
$H_{20}$      & 1.35      & 0.317     & 0.317     & 0.317      \\ \hline
\end{tabular}
\caption{Tested hypotheses for regression parameters in models with response following Poisson distribution.}
\label{tab:hipoteses_beta_poisson}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{c|cccc}
\hline
Null hypothesis & $\beta_0$ & $\beta_1$ & $\beta_2$ & $\beta_3$ \\ \hline
$H_{01}$      & 0.5       & 0         & 0         & 0         \\
$H_{02}$      & 0.250     & 0.083     & 0.083     & 0.083     \\
$H_{03}$      & 0         & 0.167     & 0.167     & 0.167     \\
$H_{04}$      & -0.25     & 0.25      & 0.25      & 0.25      \\
$H_{05}$      & -0.500    & 0.333     & 0.333     & 0.333     \\
$H_{06}$      & -0.750    & 0.417     & 0.417     & 0.417     \\
$H_{07}$      & -1.0      & 0.5       & 0.5       & 0.5       \\
$H_{08}$      & -1.250    & 0.583     & 0.583     & 0.583     \\
$H_{09}$      & -1.500    & 0.667     & 0.667     & 0.667     \\
$H_{10}$      & -1.75     & 0.75      & 0.75      & 0.75      \\
$H_{11}$      & -2.000    & 0.833     & 0.833     & 0.833     \\
$H_{12}$      & -2.250    & 0.917     & 0.917     & 0.917     \\
$H_{13}$      & -2.5      & 1.0       & 1.0       & 1.0       \\
$H_{14}$      & -2.750    & 1.083     & 1.083     & 1.083     \\
$H_{15}$      & -3.000    & 1.167     & 1.167     & 1.167     \\
$H_{16}$      & -3.25     & 1.25      & 1.25      & 1.25      \\
$H_{17}$      & -3.500    & 1.333     & 1.333     & 1.333     \\
$H_{18}$      & -3.750    & 1.417     & 1.417     & 1.417     \\
$H_{19}$      & -4.0      & 1.5       & 1.5       & 1.5       \\
$H_{20}$      & -4.250    & 1.583     & 1.583     & 1.583     \\ \hline
\end{tabular}
\caption{Tested hypotheses for regression parameters in models with response following the Bernoulli distribution.}
\label{tab:hipoteses_beta_bernoulli}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{c|cc}
\hline
Null hypothesis & $\beta_0$ & $\beta_1$ \\ \hline
$H_{01}$      & 1         & 0         \\
$H_{02}$      & 0.98      & 0.02      \\
$H_{03}$      & 0.96      & 0.04      \\
$H_{04}$      & 0.94      & 0.06      \\
$H_{05}$      & 0.92      & 0.08      \\
$H_{06}$      & 0.9       & 0.1       \\
$H_{07}$      & 0.88      & 0.12      \\
$H_{08}$      & 0.86      & 0.14      \\
$H_{09}$      & 0.84      & 0.16      \\
$H_{10}$      & 0.82      & 0.18      \\
$H_{11}$      & 0.8       & 0.2       \\
$H_{12}$      & 0.78      & 0.22      \\
$H_{13}$      & 0.76      & 0.24      \\
$H_{14}$      & 0.74      & 0.26      \\
$H_{15}$      & 0.72      & 0.28      \\
$H_{16}$      & 0.7       & 0.3       \\
$H_{17}$      & 0.68      & 0.32      \\
$H_{18}$      & 0.66      & 0.34      \\
$H_{19}$      & 0.64      & 0.36      \\
$H_{20}$      & 0.62      & 0.38      \\ \hline
\end{tabular}
\caption{Tested hypotheses for dispersion parameters.}
\label{tab:hipoteses_taus}
\end{table}

>>>>

% \jnlcitation{\cname{%
% \author{Freitas LAC}, 
% \author{Carlos LO},
% \author{Campos ACL} and 
% \author{Bonat WH}} (\cyear{2022}), 
% \ctitle{Wald test to evaluate regression and dispersion parameters in multivariate covariance generalized linear models}, \cjournal{Statistics in Medicine}}

@@

We present the dataset in \autoref{sec2}. In \autoref{sec3} we present the review of the general structure and estimation of the parameters of a McGLM, based on the ideas of Bonat and Jørgensen \cite{Bonat16}. In \autoref{sec4} our proposal is presented with the details of the Wald test to evaluate assumptions about parameters of a McGLM. In \autoref{sec5} we present the results of the performance evaluation of the proposed test based on a simulation study. In the \autoref{sec6} we apply the model and present the main results of the analysis of the data from the clinical study that aims to evaluate the use of probiotics in the control of addiction and binge eating disorder in patients undergoing bariatric surgery. Finally, the main results are discussed in \autoref{sec7}, including some directions for future investigations. The data sets and R codes are available online and can be assessed in \href{https://github.com/lineu96/paper-htmcglm}{https://github.com/lineu96/paper-htmcglm}.

@@

\begin{figure}[h]
\centerline{\includegraphics[scale = 0.9]{FIGURE1}}
\caption{Exploratory graphic analysis: (a) YFAS histogram, (b) YFAS boxplots as a function of group, (c) YFAS boxplots as a function of moment, (d) BES histogram, (b) BES boxplots as a function of group, (c) BES boxplots as a function of moment. The asterisk in the boxplots indicates the mean.\label{fig1}}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{ccccc}
\hline
\multirow{2}{*}{Group} & \multirow{2}{*}{Moment}  & \multirow{2}{*}{n} & YFAS                  & BES                   \\ \cline{4-5} 
                       &                          &                    & Mean (standard deviation) & Mean (standard deviation) \\ \hline
Placebo                & T0                       & 33                 & 0.37 (0.26)           & 0.24 (0.20)           \\
Placebo                & T1                       & 32                 & 0.11 (0.15)           & 0.09 (0.10)           \\
Placebo                & T2                       & 22                 & 0.16 (0.15)           & 0.10 (0.12)           \\
Probiotic              & T0                       & 38                 & 0.49 (0.24)           & 0.32 (0.18)           \\
Probiotic              & T1                       & 37                 & 0.09 (0.12)           & 0.10 (0.08)           \\
Probiotic              & T2                       & 22                 & 0.10 (0.14)           & 0.07 (0.09)           \\ \hline
\end{tabular}
\caption{Number of individuals, mean and standard deviation for YFAS and BES for each combination of group and time point.}
\label{tab:tab1}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{ccc}
\hline
Distribution & Link function     & Variance function \\ \hline
Normal       & Identity          & Constant           \\
Poisson      & Logarithmic       & Tweedie             \\
Bernoulli    & Logit             & Binomial            \\ \hline
\end{tabular}
\caption{Link and variance functions used in the models for each simulated distribution.}
\label{tab2}
\end{table}

@@

\begin{figure}[h]
\centerline{\includegraphics[scale = 0.9]{FIGURE2}}
\caption{Simulation study results for the regression parameters.\label{fig2}}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[scale = 0.9]{FIGURE3}}
\caption{Simulation study results for the dispersion parameters.\label{fig3}}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[scale = 0.9]{FIGURE4}}
\caption{Histogram of Pearson residuals by response.\label{fig4}}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics[scale = 0.9]{FIGURE5}}
\caption{Pearson residuals versus predicted plot with smooth trend line for each response.\label{fig5}}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{c|cccccc}
\hline
\multirow{2}{*}{Parameter} & \multicolumn{3}{c}{YFAS}                                                                                             & \multicolumn{3}{c}{BES}                                                                         \\ \cline{2-7} 
                           & Estimate & \begin{tabular}[c]{@{}c@{}}Confidence \\ interval\end{tabular} & \multicolumn{1}{c|}{p-value}        & Estimate & \begin{tabular}[c]{@{}c@{}}Confidence \\ interval\end{tabular} & p-value        \\ \hline
$\beta_0$                  & -0.54      & (-0.87;-0.22)                                                     & \multicolumn{1}{c|}{\textless 0.01} & -1.13      & (-1.44;-0.83)                                                     & \textless 0.01 \\
$\beta_1$                  & -1.55      & (-2.17;-0.94)                                                     & \multicolumn{1}{c|}{\textless 0.01} & -1.16      & (-1.62;-0.69)                                                     & \textless 0.01 \\
$\beta_2$                  & -1.13      & (-1.75;-0.51)                                                     & \multicolumn{1}{c|}{\textless 0.01} & -1.05      & (-1.58;-0.52)                                                     & \textless 0.01 \\
$\beta_3$                  & 0.49       & (0.05;0.93)                                                       & \multicolumn{1}{c|}{0.0284} & 0.37       & (-0.03;0.77)                                                      & 0.0733           \\
$\beta_4$                  & -0.73      & (-1.60;0.14)                                                      & \multicolumn{1}{c|}{0.0}            & -0.33      & (-0.96;0.30)                                                      & 0.3081           \\
$\beta_5$                  & -0.98      & (-1.93;-0.03)                                                     & \multicolumn{1}{c|}{0.0429} & -0.80      & (-1.58;-0.02)                                                     & 0.0449 \\
$\tau_0$                   & 0.18       & (0.01;0.35)                                                       & \multicolumn{1}{c|}{0.0411} & 0.17       & (0.00;0.34)                                                       & 0.0458           \\
$\tau1$                    & 0.01       & (-0.02;0.04)                                                      & \multicolumn{1}{c|}{0.5718}           & 0.04       & (-0.01;0.10)                                                      & 0.1357           \\
$p$                        & 0.91       & (0.47;1.34)                                                       & \multicolumn{1}{c|}{\textless 0.05} & 1.23       & (0.77;1.68)                                                       & \textless 0.05 \\ \hline
\end{tabular}
\caption{Parameter estimates, 95\% confidence intervals and p-values of the model.}
\label{tab3}
\end{table}

\begin{figure}[h]
\centerline{\includegraphics[width=7in,height=4in]{FIGURE6}}
\caption{Graph of model predicted for each time and group combination.\label{fig6}}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
Variable      & Degrees of freedom & Chi-square   & p-value        \\ \hline
Intercept     & 2                  & 53.1581      & \textless 0.01 \\
Moment        & 8                  & 139.0161     & \textless 0.01 \\
Group         & 6                  & 8.4928       & 0.2042         \\
Moment*Group  & 4                  & 6.9923       & 0.1363         \\ \hline
\end{tabular}
\caption{Type II multivariate analysis of variance.}
\label{tab4}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{c|c|cc|cc}
\hline
              &                    & \multicolumn{2}{c|}{YFAS}     & \multicolumn{2}{c}{BES}       \\ \hline
Variable      & Degrees of freedom & Chi-square   & p-value        & Chi-square   & p-value        \\ \hline
Intercept     & 1                  & 10.6128      & \textless 0.01 & 53.1473      & \textless 0.01 \\
Moment        & 4                  & 102.9875     & \textless 0.01 & 99.5681      & \textless 0.01 \\
Group         & 3                  & 6.6837       & 0.0827         & 5.3083       & 0.1506         \\
Moment*Group  & 2                  & 5.5984       & 0.0609         & 4.2477       & 0.1196         \\ \hline
\end{tabular}
\caption{Type II univariate analysis of variance.}
\label{tab5}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
Contrast  & Degrees of freedom & Chi-square   & p-value        \\ \hline
T0-T1     & 2                  & 97.9874      & \textless 0.01 \\
T0-T2     & 2                  & 67.2462      & \textless 0.01 \\
T1-T2     & 2                  & 2.4730       & 0.8712         \\ \hline
\end{tabular}
\caption{Two-by-two comparisons between moments for both responses.}
\label{tab6}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
Contrast                 & Degrees of freedom & Chi-square   & p-value \\ \hline
T0:Placebo-T0:Probiotic  & 2                  & 5.5819       & 0.9204  \\
T1:Placebo-T1:Probiotic  & 2                  & 0.6096       & 1       \\
T2:Placebo-T2:Probiotic  & 2                  & 1.7645       & 1       \\ \hline
\end{tabular}
\caption{Two-by-two comparisons between groups for each time point for both responses.}
\label{tab7}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
Variable               & Degrees of freedom & Chi-square & p-value        \\ \hline
$\tau_0$ & 2                  & 7.1936       & 0.0274  \\
$\tau_1$ & 2                  & 2.3201       & 0.3135         \\ \hline
\end{tabular}
\caption{Type III multivariate analysis of variance for dispersion parameters.}
\label{tab8}
\end{table}

@@

@@

\begin{table}[h]
\centering
\begin{tabular}{c|cccc}
\hline
Null hypothesis & $\beta_0$ & $\beta_1$ & $\beta_2$ & $\beta_3$ \\ \hline
$H_{01}$      & 5         & 0         & 0         & 0         \\
$H_{02}$      & 4.85      & 0.05      & 0.05      & 0.05      \\
$H_{03}$      & 4.7       & 0.1       & 0.1       & 0.1       \\
$H_{04}$      & 4.55      & 0.15      & 0.15      & 0.15      \\
$H_{05}$      & 4.4       & 0.2       & 0.2       & 0.2       \\
$H_{06}$      & 4.25      & 0.25      & 0.25      & 0.25      \\
$H_{07}$      & 4.1       & 0.3       & 0.3       & 0.3       \\
$H_{08}$      & 3.95      & 0.35      & 0.35      & 0.35      \\
$H_{09}$      & 3.8       & 0.4       & 0.4       & 0.4       \\
$H_{10}$      & 3.65      & 0.45      & 0.45      & 0.45      \\
$H_{11}$      & 3.5       & 0.5       & 0.5       & 0.5       \\
$H_{12}$      & 3.35      & 0.55      & 0.55      & 0.55      \\
$H_{13}$      & 3.2       & 0.6       & 0.6       & 0.6       \\
$H_{14}$      & 3.05      & 0.65      & 0.65      & 0.65      \\
$H_{15}$      & 2.9       & 0.7       & 0.7       & 0.7       \\
$H_{16}$      & 2.75      & 0.75      & 0.75      & 0.75      \\
$H_{17}$      & 2.6       & 0.8       & 0.8       & 0.8       \\
$H_{18}$      & 2.45      & 0.85      & 0.85      & 0.85      \\
$H_{19}$      & 2.3       & 0.9       & 0.9       & 0.9       \\
$H_{20}$      & 2.15      & 0.95      & 0.95      & 0.95      \\ \hline
\end{tabular}
\caption{Tested hypotheses for regression parameters in models with response following Normal distribution.}
\label{tab:hipoteses_beta_normal}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{c|cccc}
\hline
Null hypothesis & $\beta_0$ & $\beta_1$ & $\beta_2$ & $\beta_3$ \\ \hline
$H_{01}$      & 2.3       & 0         & 0         & 0         \\
$H_{02}$      & 2.25      & 0.017     & 0.017     & 0.017     \\
$H_{03}$      & 2.2       & 0.033     & 0.033     & 0.033     \\
$H_{04}$      & 2.15      & 0.05      & 0.05      & 0.05      \\
$H_{05}$      & 2.10      & 0.067     & 0.067     & 0.067     \\
$H_{06}$      & 2.05      & 0.083     & 0.083     & 0.083     \\
$H_{07}$      & 2         & 0.1       & 0.1       & 0.1       \\
$H_{08}$      & 1.95      & 0.117     & 0.117     & 0.117     \\
$H_{09}$      & 1.9       & 0.133     & 0.133     & 0.133     \\
$H_{10}$      & 1.85      & 0.15      & 0.15      & 0.15      \\
$H_{11}$      & 1.8       & 0.167     & 0.167     & 0.167     \\
$H_{12}$      & 1.75      & 0.167     & 0.167     & 0.167     \\
$H_{13}$      & 1.7       & 0.2       & 0.2       & 0.2       \\
$H_{14}$      & 1.65      & 0.217     & 0.217     & 0.217     \\
$H_{15}$      & 1.6       & 0.233     & 0.233     & 0.233     \\
$H_{16}$      & 1.55      & 0.25      & 0.25      & 0.25      \\
$H_{17}$      & 1.5       & 0.267     & 0.267     & 0.267     \\
$H_{18}$      & 1.45      & 0.283     & 0.283     & 0.283     \\
$H_{19}$      & 1.4       & 0.3       & 0.3       & 0.3       \\
$H_{20}$      & 1.35      & 0.317     & 0.317     & 0.317      \\ \hline
\end{tabular}
\caption{Tested hypotheses for regression parameters in models with response following Poisson distribution.}
\label{tab:hipoteses_beta_poisson}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{c|cccc}
\hline
Null hypothesis & $\beta_0$ & $\beta_1$ & $\beta_2$ & $\beta_3$ \\ \hline
$H_{01}$      & 0.5       & 0         & 0         & 0         \\
$H_{02}$      & 0.250     & 0.083     & 0.083     & 0.083     \\
$H_{03}$      & 0         & 0.167     & 0.167     & 0.167     \\
$H_{04}$      & -0.25     & 0.25      & 0.25      & 0.25      \\
$H_{05}$      & -0.500    & 0.333     & 0.333     & 0.333     \\
$H_{06}$      & -0.750    & 0.417     & 0.417     & 0.417     \\
$H_{07}$      & -1.0      & 0.5       & 0.5       & 0.5       \\
$H_{08}$      & -1.250    & 0.583     & 0.583     & 0.583     \\
$H_{09}$      & -1.500    & 0.667     & 0.667     & 0.667     \\
$H_{10}$      & -1.75     & 0.75      & 0.75      & 0.75      \\
$H_{11}$      & -2.000    & 0.833     & 0.833     & 0.833     \\
$H_{12}$      & -2.250    & 0.917     & 0.917     & 0.917     \\
$H_{13}$      & -2.5      & 1.0       & 1.0       & 1.0       \\
$H_{14}$      & -2.750    & 1.083     & 1.083     & 1.083     \\
$H_{15}$      & -3.000    & 1.167     & 1.167     & 1.167     \\
$H_{16}$      & -3.25     & 1.25      & 1.25      & 1.25      \\
$H_{17}$      & -3.500    & 1.333     & 1.333     & 1.333     \\
$H_{18}$      & -3.750    & 1.417     & 1.417     & 1.417     \\
$H_{19}$      & -4.0      & 1.5       & 1.5       & 1.5       \\
$H_{20}$      & -4.250    & 1.583     & 1.583     & 1.583     \\ \hline
\end{tabular}
\caption{Tested hypotheses for regression parameters in models with response following the Bernoulli distribution.}
\label{tab:hipoteses_beta_bernoulli}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{c|cc}
\hline
Null hypothesis & $\beta_0$ & $\beta_1$ \\ \hline
$H_{01}$      & 1         & 0         \\
$H_{02}$      & 0.98      & 0.02      \\
$H_{03}$      & 0.96      & 0.04      \\
$H_{04}$      & 0.94      & 0.06      \\
$H_{05}$      & 0.92      & 0.08      \\
$H_{06}$      & 0.9       & 0.1       \\
$H_{07}$      & 0.88      & 0.12      \\
$H_{08}$      & 0.86      & 0.14      \\
$H_{09}$      & 0.84      & 0.16      \\
$H_{10}$      & 0.82      & 0.18      \\
$H_{11}$      & 0.8       & 0.2       \\
$H_{12}$      & 0.78      & 0.22      \\
$H_{13}$      & 0.76      & 0.24      \\
$H_{14}$      & 0.74      & 0.26      \\
$H_{15}$      & 0.72      & 0.28      \\
$H_{16}$      & 0.7       & 0.3       \\
$H_{17}$      & 0.68      & 0.32      \\
$H_{18}$      & 0.66      & 0.34      \\
$H_{19}$      & 0.64      & 0.36      \\
$H_{20}$      & 0.62      & 0.38      \\ \hline
\end{tabular}
\caption{Tested hypotheses for dispersion parameters.}
\label{tab:hipoteses_taus}
\end{table}
